Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-11-25 journal paper/content/related_work.tex
Reworded/expanded Guy's new edit on LbD.

The literature on learning-by-doing vs. competition \citep[\eg][]{fudenberg1983learning, dasgupta1988learning, cabral1994learning} studies firms that learn while competing against each other, so that a firm attracting more consumers reduces its per-unit production costs. \gaedit{However, our model differs from these models in two important respects. The first is that in our model firms focus on learning product quality (as opposed to reducing production costs) and the second is that firms' current period actions have reputational consequences that directly impact consumer choices in future periods. These features are absent from traditional learning-by-doing models, but important components of a model that tries to capture data-based innovation.}

>>>>

The literature on learning-by-doing vs. competition \citep[\eg][]{fudenberg1983learning, dasgupta1988learning, cabral1994learning} studies firms that learn while competing against each other, so that a firm attracting more consumers reduces its production costs. \asedit{Our model differs in several important respects. First, firms learn to improve product quality rather than to reduce production costs. Second, the firms' current actions have consequences (via reputation and/or data collected by the algorithm) that directly impact consumer choices in the future. Third, we endogenize the technology behind learning-by-doing by explicitly considering bandit algorithms, and make comparisons between different such technologies.}

%\gaedit{However, our model differs from these models in two important respects. The first is that in our model firms focus on learning product quality (as opposed to reducing production costs) and the second is that firms' current period actions have reputational consequences that directly impact consumer choices in future periods. These features are absent from traditional learning-by-doing models, but important components of a model that tries to capture data-based innovation.}
